\section{$\epsilon$-Nets, VC-dimension}
\noindent \blue{
\textbf{1. VC-dimension of Axis-aligned rectangles.}
\\(a) Prove that no $5$ points on the plane $\mathbb{R}^2$ can be shattered by the class $C$ of axis-aligned
rectangles (that map points inside a rectangle $1$ and otherwise $0$).
}
\begin{definition}
    Given a set $X$ and a class $C$ of boolean function on $X$, 
    a subset $S \subset X$ is said to be shattered by $C$, 
    if for all subsets $U$ of $S$, there exists $f\in C$ such that for all 
    $x\in U$, $f(x) = 1$ and for all $x\in S \setminus U$, $f(x)=0$.
\end{definition}
In this problem, $X:=\mathbb{R}^k$, $C:=C_k$ is the class where each function 
corresponds to an $k$-dimension axis-aligned rectangle that labels each point inside it $1$ and otherwise $0$.
For a set $S_k$ which is a subset of $X$ that is said to be shattered by $C_k$,
if for all subsets $U_k$ of $S_k$, there exists a $k$-dimension axis-aligned rectangle such that for each point in 
$U_k$, the point is inside the $k$-dimension axis-aligned rectangle 
and for each point in set $S_k$ but not in set $U_k$, the point is not inside the  $k$-dimension axis-aligned rectangle.

\begin{proof}
    Use $S_2$ to denote any set of $5$ distinct points on the plane $\mathbb{R}^2$. 
    Let $x_{\max}$ be the maximum $x$-coordinate among the $5$ points and 
    let $x_{\min}$ be the minimum $x$-coordinate among the $5$ points.
    Use $y_{\max}$ to denote the maximum $y$-coordinate among the $5$ points and
    use $y_{\min}$ to denote the minimum $y$-coordinate among the $5$ points.
    There are at most $4$ points and at least $2$ points that contribute to  $x_{\max}$, $x_{\min}$, $y_{\max}$ and $y_{\min}$.
    Use $U_2$ to denote the set of the points that contribute to  $x_{\max}$, $x_{\min}$, $y_{\max}$ and $y_{\min}$.
    Obviously, $U_2\subsetneq S_2$. 
    Since $U_2$ is the set of points that contribute to  $x_{\max}$, $x_{\min}$, $y_{\max}$ and $y_{\min}$,
    if a 2-dimension axis-aligned rectangle contions all points in set $U_2$, it must contion all points in $S_2$.
    Then for set $U_2$, there is no such 2-dimension axis-aligned rectangle can satisfy the two constrains at the same time:
    \begin{enumerate}
        \item For each point in set $U$, the point is inside the axis-aligned rectangle.
        \item  For each point in set $S$ but not in set $U$, the point is not inside the axis-aligned rectangle.
    \end{enumerate}

    Thus, no $5$ points on the plane $\mathbb{R}^2$ can be shattered by the class $C$ of axis-aligned
    rectangles.
\end{proof}
\noindent \blue{
(b) Compute the VC-dimension of the class $C_k$ of $k$-dimension axis-aligned rectangles in $\mathbb{R}^k$.
In particular, you need to find a number $d$ such that there exist $d$ points in $\mathbb{R}^k$ that can be shattered by the $C_k$, and
prove that any $d+1$ points in $\mathbb{R}^k$ cannot be shattered by $C_k$.}\\
The VC-dimension of the class $C_k$ of $k$-dimension axis-aligned rectangles in $\mathbb{R}^k$ is $2k$.
\begin{proof}
    \noindent
    \begin{enumerate}
        \item  There exists $2k$ points in $\mathbb{R}^k$ that can be shattered by the $C_k$.
        
    A possible set of the $2k$ points is as follows and use $S^\prime_k$ to denote it.
    \begin{align}
        \nonumber S^\prime_k=&\{(1,0,0,...,0),(-1,0,0,...0),(0,1,0,...0),(0,-1,0,...,0),\\
        \nonumber &(0,0,1,...,0),(0,0,-1,...,0),...,(0,0,0,...,1),(0,0,0,...,-1)\}
    \end{align}

    Use $U^\prime_k$ to denote any subset of $S^\prime_k$.
    Since any point in $S^\prime_k$ can provide the minimum or maximum value in a dimension,
    for  each subset $U^\prime_k$ of $S^\prime_k$, we can always find a $k$-dimension axis-aligned rectangle such that 
    all points in $U^\prime_k$ are inside the $k$-dimension axis-aligned rectangle and 
    all points in set $S^\prime_k$ but not in set $U^\prime_k$ are not inside the $k$-dimension axis-aligned rectangle.
    Thus we have that there exist $2k$ points in $\mathbb{R}^k$ that can be shattered by the $C_k$.
    \item Any $2k+1$ points in $\mathbb{R}^k$ cannot be shattered by $C_k$.

    Use $S_k$ to denote any set of $2k+1$ distinct points in $\mathbb{R}^k$.
    Use set $U_k$ to denote the set of points that can contribute the maximum or minimum value in each dimension among points in set $S_k$.
    Obviously, $|U_k|\in[2,2k]$ and $U_k\subsetneq S_k$.
    Since $U_k$ is the set of points that can contribute the maximum or minimum value in each dimension,
    if a $k$-dimension axis-aligned rectangle contions all points in set $U_k$, it must contion all points in $S_k$.
    Then for set $U_k$, there is no such $k$-dimension axis-aligned rectangle can satisfy the two constrains at the same time:
    \begin{enumerate}
        \item For each point in set $U_k$, the point is inside the $k$-dimension axis-aligned rectangle.
        \item  For each point in set $S_k$ but not in set $U_k$, the point is not inside the $k$-dimension axis-aligned rectangle.
    \end{enumerate}

    Thus, no $2k+1$ points in $\mathbb{R}^k$ can be shattered by the class $C_k$ of $k$-dimension axis-aligned rectangles.
\end{enumerate}
   
By definition, the VC-dimension of $(X, C)$ is the maximum cardinality of a subset $S \subseteq X$ that is shattered by $C$.
Hence, in this problem, the VC-dimension of the class $C_k$ of $k$-dimension axis-aligned rectangles in $\mathbb{R}^k$ is $2k$.
\end{proof}
\noindent \blue{2. \textbf{Conditional Expectation.}\\
Suppose $Y:\Omega\rightarrow\mathbb{R}$ is a random variable and
$W:\Omega\rightarrow\mathcal{U}$ is a random object 
defined on the same probability space $(\Omega, \mathcal{F},Pr)$.
Prove that $\mathbb{E}[Y]=\mathbb{E}[\mathbb{E}[Y|W]]$.
You may assume that both $\Omega$ and $\mathcal{U}$ are finite.
}